\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-11-28 projects/project_5/molecular_dynamics/article/article.tex
on diffusion now

We are now interested in determining what initial temperature $T_i$ is needed
in order to have a final temperature of $T$.  One way of examining this is by
looking at the ratio $T/T_i$. 
\subsection{Melting temperature of system}
\label{sub:melting_temperature_of_system}

@@

\bibitem{min_image}
    \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention}
\bibitem{equipar}
    \url{https://en.wikipedia.org/wiki/Equipartition\_theorem}
\end{thebibliography}

>>>>

We are now interested in determining what initial temperature $T_i$ is needed
in order to have a final temperature of $T$.  One way of examining this is by
looking at the ratio $T/T_i$. As we can see in \ref{fig:temperature_ratio} the
ratio stabilizes around $T/T_i = 0.5$. Solving this for $T_i$ tells us that if
we are interested in a final temperature of $T$, then we should chose our
initial temperature to be
\begin{equation}
    \notag
    T_i = 2T.
\end{equation}

As we see from the plot, the temperature drastically drops just after the
initial state. This is because $T \propto E_k$, i.e., the temperature is
proportional to the kinetic energy, and since the potential has not yet kicked
in, the kinetic energy is at its maximum. While what we have just observed is
an empirical result, we can alternatively look at the virial theorem
\cite{virial}, which relates the time average of the kinetic energy to the time
average of the potential energy. This gives us a description of this
stabilization independent of the temperature.

\begin{figure}[h]
    \centering \includegraphics[width=0.8\linewidth]{temperature_ratio.pdf}
    \caption[Temperature ratio]{Plotting the ratio between initial and
        instantaneous temperature for varying $T_i$. Here the initial
        temperatures ranges from 20 to 500 kelvin, with 48 intermediate steps.
    As we can see the ratio stabilizes around 0.5. The graph of an arbitrary
temperature has been highlighted in black.}
    \label{fig:temperature_ratio}
\end{figure}

\subsection{Melting temperature of system}
\label{sub:melting_temperature_of_system}

@@

\bibitem{min_image}
    \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention}
\bibitem{equipar}
    \url{https://en.wikipedia.org/wiki/Equipartition\_theorem}
\bibitem{virial}
    \url{https://en.wikipedia.org/wiki/Virial_theorem#Time_averaging}
\end{thebibliography}
